### 2020-06-29 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
OptLet правки списка литературы

\bibitem{c7} Figueira,J., Greco, S., Ehrgott, M., editors.: Multiple criteria decision analysis: State of the art surveys. Springer, New York (NY). (2005)

@@

\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., editors.: Multi-Objective Optimization--Interactive and Evolutionary Approaches. Springer, Berlin. (2008)

@@

\bibitem{c18} Strongin, R., Sergeyev, Ya.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht. (2nd ed. 2013, 3rd ed. 2014).

@@

\bibitem{c26} Lera D., Sergeyev Ya.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Commun. Nonlinear Sci. \textbf{23}(1-3), 328--342 (2015)

@@

\bibitem{c33} Kvasov D.E., Sergeyev Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Adv. Eng. Softw. \textbf{80}, 58--66 (2015)

@@

\bibitem{c37} Gaviano, M., Kvasov, D.E, Lera, D., and Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Trans. Math. Softw. \textbf{29}(4), 469--480 (2003)

@@

\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Digabel, S.Le, Salomon, L.: Performance indicators in multiobjective optimization. G-2018-90, (2018)

@@

\bibitem{c54} Hansen, N., Auger, A., Finck, S., and Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay-Ile-de-France. updated February 2010 (2009)

>>>>

\bibitem{c7} Figueira,J., Greco, S., Ehrgott, M., (eds.): Multiple criteria decision analysis: State of the art surveys. Springer, New York (NY). (2005)

@@

\bibitem{c10} Branke, J., Deb, K., Miettinen, K., Slowinski, R., (eds.): Multi-Objective Optimization--Interactive and Evolutionary Approaches. Springer, Berlin. (2008)

@@

\bibitem{c18} Strongin, R.G., Sergeyev, Y.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht. (2nd ed. 2013, 3rd ed. 2014).

@@

\bibitem{c26} Lera, D., Sergeyev, Y.D.: Deterministic global optimization using space-filling curves and multiple estimates of Lipschitz and Holder constants. Commun. Nonlinear Sci. \textbf{23}(1-3), 328--342 (2015)

@@

\bibitem{c33} Kvasov, D.E., Sergeyev, Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Adv. Eng. Softw. \textbf{80}, 58--66 (2015)

@@

\bibitem{c37} Gaviano, M., Kvasov, D.E, Lera, D., Sergeyev, Y.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM Trans. Math. Softw. \textbf{29}(4), 469--480 (2003)

@@

\bibitem{c52} Audet, C., Bigeon, J., Cartier, D., Digabel, S.Le, Salomon, L.: Performance indicators in multiobjective optimization. Technical Report G-2018-90, Les cahiers du GERAD. (2018)

@@

\bibitem{c54} Hansen, N., Auger, A., Finck, S., Ros, R.: Real-Parameter Black-Box Optimization Benchmarking 2009: Experimental Setup. INRIA Research Report RR-6829, INRIA Saclay-Ile-de-France. updated February 2010 (2009)
